### 2015-03-13 ThesisJo/derivations.tex
la2pdf commit - 2015:03:10	15:06:05	(Tue10.Mar)
la2pdf commit - 2015:03:12	14:05:15	(Thu12.Mar)
la2pdf commit - 2015:03:12	17:16:15	(Thu12.Mar)
la2pdf commit - 2015:03:13	13:56:37	(Fri13.Mar)
la2pdf commit - 2015:03:13	14:29:03	(Fri13.Mar)

Now let us choose a trigonometric window function:
%
\begin{align}
\w = e^{j\phi_\theta[m]}\frac{1}{2\pi\alpha?}\big(\alpha + (1-\alpha)\sin\left(\frac{2\pi m}{M-1}\right)\big)
\end{align}
%
where $\phi_\theta[m] = \frac{2\pi}{\lambda}dm\sin\theta$. Inserting this yields:
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\phi_\theta[m]}\Big(\alpha + (1-\alpha)\sin\left(\frac{2\pi m}{M-1}\right)\Big) x_m^* \nn
&= \alpha\sumb{m=0}{M-1} e^{j\phi_\theta[m]} x_m^* + (1-\alpha)\sumb{m=0}{M-1} e^{j\varphi[m]}\sin\left(\frac{2\pi m}{M-1}\right) x_m^* \\
&= \alpha \a + (1-\alpha)\b
\end{align}
%
where:
%
\begin{align}
a = \sumb{m=0}{M-1} e^{j\phi_\theta[m]}x_m^* \qquad \text{and} \qquad b_m = \sumb{m=0}{M-1} e^{j\phi_\theta[m]}\sin\left(\frac{2\pi m}{M-1}\right)x_m^*
\end{align}
%
where
%
\begin{align}
|\w\H\x|^2 &= \Big| \alpha a + (1-\alpha)b \Big|^2 \nn
&= \Big[\alpha a + (1-\alpha)b\Big] \Big[\alpha a^* + (1-\alpha)b^*\Big] \nn
&= \alpha^2 aa^* + \alpha a(1-\alpha)b^* + \alpha a^*(1-\alpha)b + (1-\alpha)^2bb^* \nn
&= \alpha^2 aa^* + \alpha(1-\alpha)(ab^* + a^*b) + (1-\alpha)^2bb^* \nn
&= \alpha^2 (aa^* - (ab^* + a^*b) - bb^*) + \alpha(ab^* + a^*b) + bb^* \nn
\end{align}
%

@@

>>>>

Now let us choose a trigonometric window function:
%
\begin{align}
\w = e^{j\phi_\theta[m]}\big(\alpha - (1-\alpha)\cos\left(\frac{2\pi m}{M-1}\right)\big)
\end{align}
%
where $\phi_\theta[m] = \frac{2\pi}{\lambda}dm\sin\theta$. Inserting this yields:
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\phi_\theta[m]}\Big(\alpha - (1-\alpha)\cos\left(\frac{2\pi m}{M-1}\right)\Big) x_m^* \nn
&= \alpha\sumb{m=0}{M-1} e^{j\phi_\theta[m]} x_m^* + (1-\alpha)\sumb{m=0}{M-1} e^{j\varphi[m]}\sin\left(\frac{2\pi m}{M-1}\right) x_m^* \\
&= \alpha \a\T\x + (1-\alpha)\b\T\x
\end{align}
%
where:
%
\begin{align}
\a = \begin{bmatrix}
     1 \\
     e^{j\frac{2\pi}{\lambda}d\sin\theta} \\
     e^{j\frac{2\pi}{\lambda}2d\sin\theta} \\
     \vdots \\
     e^{j\frac{2\pi}{\lambda}d(M-1)\sin\theta}
     \end{bmatrix} \qquad \text{and} \qquad
\b = \begin{bmatrix}
     0 \\
     e^{j\frac{2\pi}{\lambda}d\sin\theta}\sin\left(\frac{2\pi m}{M-1}\right) \\
     e^{j\frac{2\pi}{\lambda}2d\sin\theta}\sin\left(\frac{2\pi m}{M-1}\right) \\
     \vdots \\
     0
     \end{bmatrix}
\end{align}
%
To attain unity gain in the look direction the weights must sum to one. 
%
\begin{align}
\w\T\1 &= \big(\alpha\a - (1-\alpha)\b\big)\T\1 = 1
\end{align}
%
This is true for any value of $\alpha$ if $\a\T\1 = 1$ and $\b\T\1 = 1$.

where
%
\begin{align}
|\w\H\x|^2 &= \Big| \alpha a + (1-\alpha)b \Big|^2 \nn
&= \Big[\alpha a + (1-\alpha)b\Big] \Big[\alpha a^* + (1-\alpha)b^*\Big] \nn
&= \alpha^2 aa^* + \alpha a(1-\alpha)b^* + \alpha a^*(1-\alpha)b + (1-\alpha)^2bb^* \nn
&= \alpha^2 aa^* + \alpha(1-\alpha)(ab^* + a^*b) + (1-\alpha)^2bb^* \nn
&= \alpha^2 (aa^* - (ab^* + a^*b) - bb^*) + \alpha(ab^* + a^*b) + bb^* \nn
\end{align}
%
\begin{align}
\frac{\partial}{\partial\alpha} |\w\H\x|^2 
&= 2\alpha (aa^* - (ab^* + a^*b) - bb^*) + ab^* + a^*b = 0
\end{align}
%
\begin{align}
\alpha &= \frac{ab^* + a^*b}{2(aa^* - (ab^* + a^*b) - bb^*)}
\end{align}

@@

\subsection{Element}

The frequency response of an element is is given by the Fourier transform of the element's window function.
%
\begin{align}
W(\k) = \int\limits_{V} w(\p)\,e^{-j\k\dot\p} dV
\end{align}
%
where $\p = \bmat{x & y & z}\T$ and $dV = dx\,dy\,dz$. For a rectangular 2D element spanning the xy-plane, having sides with length $d_x$ and $d_y$, the frequency response becomes:
%
\begin{align}
W_\text{rect}(k_x, k_y) = \frac{\sin\frac{k_x\,d_x}{2}}{\frac{k_x\,d_x}{2}}
\end{align}
%
If we assume a rectangular
